\glossarystyle{altlist}
\makeglossaries

\defineglossary{encoding}{
  A particular interpretation of a sequence of bytes into distinguishable \gpl{character}.
}

\defineglossary{character}{
  A singular entity as specified by an \g{encoding}.
}

\defineglossary{alphabetic}{
  Any \g{character} that is one of the following: \\
  {\ttfamily
    \unicode{61} \unicode{62} \unicode{63} \unicode{64} \unicode{65}\\
    \unicode{66} \unicode{67} \unicode{68} \unicode{69} \unicode{6A}\\
    \unicode{6B} \unicode{6C} \unicode{6D} \unicode{6E} \unicode{6F}\\
    \unicode{70} \unicode{71} \unicode{72} \unicode{73} \unicode{74}\\
    \unicode{75} \unicode{76} \unicode{77} \unicode{78} \unicode{79}\\
    \unicode{7A} \unicode{41} \unicode{42} \unicode{43} \unicode{44}\\
    \unicode{45} \unicode{46} \unicode{47} \unicode{48} \unicode{49}\\
    \unicode{4A} \unicode{4B} \unicode{4C} \unicode{4D} \unicode{4E}\\
    \unicode{4F} \unicode{50} \unicode{51} \unicode{52} \unicode{53}\\
    \unicode{54} \unicode{55} \unicode{56} \unicode{57} \unicode{58}\\
    \unicode{59} \unicode{5A}}
}

\defineglossary{numeric}{
  Any \g{character} that is one of the following: \\
  {\ttfamily
    \unicode{30} \unicode{31} \unicode{32} \unicode{33} \unicode{34}\\
    \unicode{35} \unicode{36} \unicode{37} \unicode{38} \unicode{39}}
}

\defineglossary{alphanumeric}{
  Any \g{character} that is either \g{alphabetic} or \g{numeric}.
}

\defineglossary{whitespace}{
  Any \g{character} that represents a horizontal gap. Examples include space, tab, zero-width space, etc.
}

\defineglossary{character class}{
  A specified set of \gpl{character}.
}

\defineglossary{hexadecimal number}{
  A sequence of \gpl{character} that are one of the following and thus form a mathematical number in base-16/hexadecimal representation. \\
  {\ttfamily
    \unicode{30} \unicode{31} \unicode{32} \unicode{33} \unicode{34}\\
    \unicode{35} \unicode{36} \unicode{37} \unicode{38} \unicode{39}\\
    \unicode{61} \unicode{62} \unicode{63} \unicode{64} \unicode{65} \unicode{66}\\
    \unicode{41} \unicode{42} \unicode{43} \unicode{44} \unicode{45} \unicode{46}}
}

\defineglossary{decimal number}{
  A sequence of \gpl{character} that are \g{numeric} and thus form a mathematical number in base-10/decimal representation.
}

\defineglossary{real number}{
  A sequence of \gpl{character} as follows: One or more \g{numeric} \gpl{character}, optionally followed by a \inline$.$ dot, followed by an arbitrary number of \g{numeric} \gpl{character}. This forms a mathematical real number in base-10/decimal representation where the dot denotes the decimal point.
}

\defineglossary{case insensitive}{
  When both the lower- and upper-case representation of an \g{alphabetic} \g{character} are treated as \g{equivalent}.
}

\defineglossary{string}{
  A sequence of \gpl{character}.
}

\defineglossary{substring}{
  A sequence of \gpl{character} within a \g{string}.
}

\defineglossary{text}{
  Text is made up of a series of \gpl{string} and \gpl{textual component}.
}

\defineglossary{textual component}{
  A section of \g{text} with specific visual \glink{style}{styling}, representation, and interaction properties.
}

\defineglossary{specified textual component}{
  A \g{textual component} that is declared in this specification.
}

\defineglossary{resulting textual component}{
  The \g{textual component} that the \g{directive} puts in place of the \g{identifier} in the \g{document}.
}

\defineglossary{current component}{
  The \g{textual component} with the highest \g{level} that the \g{position} is in.
}

\defineglossary{style}{
  A \g{style} is an attribute of a \g{textual component} that specifies how the \g{textual component} and its contents are supposed to be visually represented in the \g{document}.
}

\defineglossary{format}{
  A particular representation of data.
}

\defineglossary{document}{
  1) The top-most \g{textual component} that is not contained in any other \g{textual component}.
  2) A \g{string} to be interpreted into a \g{textual component} using rules outlined by \gpl{directive}.
}

\defineglossary{document format}{
  A set of grammar and semantics to \glink{interpretation}{interpret} the contents of a \g{document}.
}

\defineglossary{page}{
  Every \g{document} consists of one or more \gpl{page}. A page is a container of some physical size within which \g{text} is displayed.
}

\defineglossary{newline}{
  Any \g{character} that represents that a new line should be started.
}

\defineglossary{escaping}{
  If a \g{character} is preceded by \unicode{5C}, it is ``escaped'' and its semantic meaning is suppressed.
}

\defineglossary{line}{
  Any sub-sequence within a \g{string} that is delimited by an \glink{escaping}{unescaped} \g{newline}. That is to say, a line always begins at either the beginning of the \g{string} or after the \g{newline}, and always ends at either the end of the \g{string} or with a \g{newline} that is not preceded by the \unicode{5C} \g{character}.
}

\defineglossary{empty line}{
  A \g{line} that only contains \g{whitespace} and a \g{newline}, or a sole \g{newline}.
}

\defineglossary{match}{
  A \g{match} occurs if a \g{string} is exactly recognised by some specific pattern or method.
}

\defineglossary{full match}{
  A \g{full match} occurs if a \g{match} occurs and the \g{cursor} is located immediately after the matched \g{string}.
}

\defineglossary{identifier}{
  Some form of pattern or method by which a \g{string} is recognisable. More specifically, an \g{identifier} provides a means by which a \g{substring} can be distinguished from the rest of the \g{string}. 
}

\defineglossary{identifier specifier}{
  A pattern in \sectionref{identifier syntax} to specify the way in which the \g{identifier} can be recognised.
}

\defineglossary{directive}{
  A directive specifies what happens when the \g{implementation} \glink{match}{matches} a particular \g{identifier}. In particular, it may specify how the input \g{string} is \glink{interpretation}{interpreted} into \g{text} in the \g{document}.
}

\defineglossary{line directive}{
  A \g{directive} that spans one or more \gpl{line} as specified in \sectionref{line directives}.
}


\defineglossary{singular line directive}{
  A \g{line directive} as specified in \sectionref{singular line directives}.
}

\defineglossary{spanning line directive}{
  A \g{line directive} as specified in \sectionref{spanning line directives}.
}

\defineglossary{guarded line directive}{
  A \g{line directive} as specified in \sectionref{guarded line directives}.
}

\defineglossary{inline directive}{
  A \g{directive} that can appear at any point within a \g{string} as specified in \sectionref{inline directives}.
}

\defineglossary{surrounding inline directive}{
  An \g{inline directive} as specified in \sectionref{surrounding inline directives}.
}

\defineglossary{entity inline directive}{
  An \g{inline directive} as specified in \sectionref{entity inline directives}.
}

\defineglossary{compound inline directive}{
  An \g{inline directive} as specified in \sectionref{compound inline directives}.
}

\defineglossary{equivalent}{
  Two objects are considered equivalent, if they denote the same meaning or idea. In specific, two \gpl{character} are equivalent, if they denote the same visual identity.
}

\defineglossary{interpretation}{
  The act of detecting \gpl{directive} and executing their effects on a \g{document}.
}

\defineglossary{processing}{
  The act of evaluating a \g{directive} on a \glink{match}{matched} \g{string} and translating it into either effects on the \g{parser state} or \gpl{resulting textual component}.
}

\defineglossary{parser state}{
  A set of information that the \g{implementation} keeps during \g{interpretation}.
}

\defineglossary{implementation}{
  Some form of program or system that implements the semantics of Markless.
}

\defineglossary{implementation dependant}{
  The exact implications are up to the \g{implementation} to decide, but must be clearly defined.
}

\defineglossary{conforming implementation}{
  An \g{implementation} that fully and correctly adheres to all requirements laid down by this specification. An \g{implementation} may support additional features not described in this specification and still be conforming, as long as none of the features interfere with the \g{interpretation} of a \g{conforming document}.
}

\defineglossary{conforming document}{
  A \g{document} that does not violate any of the requirements set forth by the \gpl{directive} outlined in this specification and can thus be properly \glink{interpretation}{interpreted} by any \g{conforming implementation}.
}

\defineglossary{level}{
  A number representing the depth of a \g{directive} within the \g{document}. The level within any \g{directive} is one higher than the level the \g{directive} itself is at. The level of the \g{document} is always 0.
}

\defineglossary{binding}{
  A \syntax{binding} syntax rule, the content of which is the \g{string} it \glink{match}{matches}.
}

\defineglossary{content binding}{
  A \g{binding} with the \syntax{name} \inline$content$.
}

\defineglossary{user}{
  Some entity ---usually a human--- that can view and interact with a \g{document}.
}

\defineglossary{action}{
  Some form of interaction that a \g{user} viewing a \g{document} can perform.
}

\defineglossary{label}{
  1) A unique name within a \g{document} that is associated with a single \g{textual component} of the \g{document}. 
  2) A \g{textual component} that is associated through a \g{label}.
}

\defineglossary{disabled directive}{
  1) A \g{directive} on the \g{implementation}'s internal list of disabled directives.
  2) A \g{directive} whose \gpl{identifier} must not be recognised.
  3) A \g{directive} that cannot be contained in the \g{current component}.
}

\defineglossary{error}{
  A message that indicates a problem with the \g{document} that makes it unable for the \g{interpretation} to proceed. When \glink{signalling}{signalled}, the \g{implementation} must abort \g{interpretation} without producing a resulting \g{document}.
}

\defineglossary{warning}{
  A message that indicates a potential problem that occurred during \g{interpretation} that might cause the resulting \g{document} to appear wrong.
}

\defineglossary{signalling}{
  The act by which an \g{implementation} can display a message to the \g{user}.
}

\defineglossary{line break mode}{
  A \g{variable} of the name \inline$line-break$ that specifies how \g{newline} \gpl{character} are \glink{interpretation}{interpreted} into the output \g{text} of the \g{document}. Only four values are permitted: \inline$always$, \inline$never$, \inline$escaped$, and \inline$unescaped$.
}

\defineglossary{instruction}{
  An instance of the \sectionref{instruction} \g{directive}.
}

\defineglossary{position}{
  A marker for where the \g{implementation} is in the resulting \g{document} during \g{interpretation}.
}

\defineglossary{cursor}{
  A marker for where the \g{implementation} is in the inputting \g{document} during \g{interpretation}.
}

\defineglossary{variable}{
  A name associated with some internal state of the \g{implementation}.
}

\defineglossary{standard processing loop}{
  The algorithm to \glink{processing}{process} a \g{document} as described in \sectionref{parser steps}.
}

%%% Local Variables:
%%% mode: latex
%%% TeX-master: "markless"
%%% TeX-engine: luatex
%%% TeX-command-extra-options: "-shell-escape"
%%% End:
